Nanophotonic Computational Design

### 2013-02-20 defense/pres2.tex
Getting there...

\oursection{Iterative design of nanophotonic devices}
\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2 
    \end{align*}
\I  Takes advantage of the \emph{bi-linearity} of the physics residual
    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
\nextpage

\I  More concisely, we iteratively solve the following
    \BE \minimize_\text{alternately $x$ then $z$} 
        \|A(z)x - b\|^2 + \eta_0\|z - z_0\|^2 + \eta_1\|x-x_0\|^2 \EE
\I  Design process now consists of \emph{multiple} computational steps
    \BI $\eta_0, \eta_1$ gradually decreased to bring physics residual toward 0 \EI
\nextpage

@@

\oursection{Iterative design with hard constraints on $z$}
\I  We can also put hard limits on $z$ (structure)
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_0\|^2\\
    \subto & z_\text{min} \le z \le z_\text{max}
    \end{align*}
\I  $z_\text{min} \le z \le z_\text{max}$ constraint 
    better represents manufacturability constraint
    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
\nextpage

\smallfig{1d_hardlimit}
\I  Final  
\nextpage

\I  higher dimensions
\myfig{2d_circ}{5}
\myfig{25d_circ}{5}
\nextpage

\oursection{Objective-first design of nanophotonic devices}
\I  Next step in our thinking is that for most devices only some parts of the field matter
\I  waveguiding devices
\medfig{ob1_wg}

\oursection{Design of 3D nanophotonic devices}

>>>>

\oursection{Iterative design of nanophotonic devices}
\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2 
    \end{align*}
\I  Takes advantage of the \emph{bi-linearity} of the physics residual
    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
\nextpage

\I  More concisely, we iteratively solve the following
    \BE \minimize_\text{alternately $x$ then $z$} 
        \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2
                        + \eta_1\|x-x_\text{prev}\|^2 \EE
\I  Design process now consists of \emph{multiple} computational steps
    \BI $\eta_0, \eta_1$ gradually decreased to bring physics residual toward 0 \EI
\nextpage

@@

\oursection{Iterative design with hard constraints on $z$}
\I  We can also put hard limits on $z$ (structure)
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2\\
    \subto & z_\text{min} \le z \le z_\text{max}
    \end{align*}
\I  $z_\text{min} \le z \le z_\text{max}$ constraint 
    better represents manufacturability constraint
    \BI Corresponds to a minimum and maximum allowable permittivity ($\epsilon$) \EI
\nextpage

\smallfig{1d_hardlimit}
\I  Well-behaved, manufacturable $z$ (structure)
\I  Final $x$ (field) accurately reproduced
\I  Majority of elements of $z$ are fortuitously at one limit or the other!
\nextpage

\I  Can be used to create 2D resonators
\smallfig{2d_circ}
\nextpage

\I  3D resonators can be designed using a ``2.5D'' approximation
\smallfig{25d_circ}
\nextpage

\oursection{Objective-first design of linear devices}
\I  Next realization: for linear components, 
    only certain elements of $x$ (field) matter
    \BI Specifically, the elements of $x$ at the input/output ports \EI
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 \\
    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
        & z_\text{min} \le z \le z_\text{max}
    \end{align*}
\I  Instead of regularization term, we force the elements of $x$
    at the boundary to be equal to the ideal case ($\hat{x}$)
\nextpage

\I  Applied to the design of 2D waveguide mode couplers
\smallfig{ob1_explanation}
\I  Produced designs which exhibited
    \BI High efficiency ($\sim 98\%$)
    \I  Small device footprints ($1.5-4$ square vacuum wavelengths) \EI
\nextpage

\I  Coupler to wide, low-index waveguide
\medfig{ob1_wg}
\nextpage

\I  Coupler from fundamental to second-order waveguide mode
\medfig{ob1_wg2}
\nextpage

\oursection{Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  Goal: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, manufacturable structure \EI
\nextpage

\I  Problem: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
    \BI Millions of variables
    \I  Famously ill-conditioned 
    \I  No known commercial \emph{solvers} that can handle arbitrary structures \EI
\pause
\smallfig{wonseok}
\I  Fortunately, Wonseok had already solved this problem

\oursection{Maxwell: Light-simulation supercomputer}
\I  Partnered with Wonseok to develop a cloud-based electromagnetic solver 
    using Amazon Web Services 
    \BI GPU-accelerated implementation of Wonseok's algorithm
    \I  Cluster scales automatically to tens of nodes \EI
\nextpage

\I  Scalable
    \BI Far outstrips computing clusters such as Teragrid
    \I  Can perform multiple solves in parallel, on a single Matlab instance 
    \I  All computation is performed externally (in the cloud) \EI

\I  Easy to use
    \BI Installs with a single Matlab command
    \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI

\I  The key technological enabler ...
